\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-05-06 sections/supplementary.tex
Change: Update the Methods for draft v2

  Fisher~\cite{fisher_224a_1948} proposed that for $w$ independent p-values, each generated by $w$ different methods and denoted by $\bar{P}^i$, the following will hold true for the statistic $\Psi$:
  \begin{equation*}
    \begin{aligned}
      \Psi &= \sum_{i=1}^w -2 \log \left( \bar{P}^i \right) \\
        \Psi &\sim \chi^2_{2w}
    \end{aligned}
  \end{equation*}

  Brown~\cite{brown_400_1975} extended Fisher's method to dependent p-values by using a re-scaled $\chi^2$ distribution:
  \begin{equation*}
    \Psi \sim c \chi^2_{2f}
  \end{equation*}
  where, $f$ is the degrees of freedom and $c$ is the scale factor and are given by:
  \begin{equation*}
    f = \frac{\mathrm{E}[\Psi]^2}{\mathrm{Var}[\Psi]} ~~~\text{and}~~~ c = \frac{\mathrm{Var}[\Psi]}{2\mathrm{E}[\Psi]} = \frac{w}{f}
  \end{equation*}

  Furthermore, Brown showed that $\mathrm{E}[\Psi]$ and $\mathrm{Var}[\Psi]$ can be calculated via a numerical integration:
  \begin{equation*}
    \mathrm{E}[\Psi] = 2w ~~~\text{and}~~~ \mathrm{Var}[\Psi] = 4w + 2\sum_{i<j} \mathrm{Cov}\left( -2\log(\bar{P}^i), -2\log(\bar{P}^j) \right)
  \end{equation*}

  Kost and McDermott~\cite{kost_combining_2002} further fit a third-order polynomial to approximate the covariance
  \begin{equation}
    \mathrm{Cov}\left( -2\log(\bar{P}^i), -2\log(\bar{P}^j) \right) \approx 3.263 \rho_{ij} + 0.710 \rho_{ij}^2 + 0.027 \rho_{ij}^3
    \label{eqn:covariance-pvalues}
  \end{equation}
  where, $\rho_{ij}$ is the correlation between method $i$ and method $j$

  The final combined p-value~\cite{Poole_Gibbs_Shmulevich_Bernard_Knijnenburg_2016} is then given by:
  \begin{equation}
    \begin{aligned}
        & \hat{P}_j = 1.0 - \Phi_{2f}\left( \psi / c \right) \\
        \text{where},~ &\psi = -2 \sum_{i=1}^w \log(\bar{P}^i_j) ~~~\text{and}~~~ \Phi_{2f} = \mathrm{CDF}\left( \chi^2_{2f} \right)
    \end{aligned}
    \label{eqn:pvalue-combined}
  \end{equation}

  The p-value merging and consensus method in \ac{micone} (refer Documentation) uses Equation~\ref{eqn:covariance-pvalues} to estimate the covariance of the pvalues and Equation~\ref{eqn:pvalue-combined} to merge the p-values (obtained from bootstrapping) from the different correlation methods.
  Note that we do not use Pearson and Spearman methods in the p-value merging step and these algorithms are only used for demonstration and comparison.
  The combined p-values are used to threshold for significance during the consensus network step.

>>>>

  Fisher~\cite{fisher_224a_1948} proposed that for $k$ independent p-values, each generated by $k$ different methods and denoted by $\bar{P}^i$, the following will hold true for the statistic $\Psi$:
  \begin{equation*}
    \begin{aligned}
      \Psi &= \sum_{i=1}^k -2 \log \left( \bar{P}^i \right) \\
        \Psi &\sim \chi^2_{2k}
    \end{aligned}
  \end{equation*}

  Brown~\cite{brown_400_1975} extended Fisher's method to dependent p-values by using a re-scaled $\chi^2$ distribution:
  \begin{equation*}
    \Psi \sim c \chi^2_{2f}
  \end{equation*}
  where, $f$ is the degrees of freedom and $c$ is the scale factor and are given by:
  \begin{equation*}
    f = \frac{\mathrm{E}[\Psi]^2}{\mathrm{Var}[\Psi]} ~~~\text{and}~~~ c = \frac{\mathrm{Var}[\Psi]}{2\mathrm{E}[\Psi]} = \frac{k}{f}
  \end{equation*}

  Furthermore, Brown showed that $\mathrm{E}[\Psi]$ and $\mathrm{Var}[\Psi]$ can be calculated via a numerical integration:
  \begin{equation*}
    \mathrm{E}[\Psi] = 2k ~~~\text{and}~~~ \mathrm{Var}[\Psi] = 4k + 2\sum_{i<j} \mathrm{Cov}\left( -2\log(\bar{P}^i), -2\log(\bar{P}^j) \right)
  \end{equation*}

  Kost and McDermott~\cite{kost_combining_2002} further fit a third-order polynomial to approximate the covariance
  \begin{equation}
    \mathrm{Cov}\left( -2\log(\bar{P}^i), -2\log(\bar{P}^j) \right) \approx 3.263 \rho_{ij} + 0.710 \rho_{ij}^2 + 0.027 \rho_{ij}^3
    \label{eqn:suppl_covariance-pvalues}
  \end{equation}
  where, $\rho_{ij}$ is the correlation between method $i$ and method $j$

  The final combined p-value~\cite{Poole_Gibbs_Shmulevich_Bernard_Knijnenburg_2016} is then given by:
  \begin{equation}
    \begin{aligned}
        & \hat{P}_j = 1.0 - \Phi_{2f}\left( \psi / c \right) \\
        \text{where},~ &\psi = -2 \sum_{i=1}^k \log(\bar{P}^i_j) ~~~\text{and}~~~ \Phi_{2f} = \mathrm{CDF}\left( \chi^2_{2f} \right)
    \end{aligned}
    \label{eqn:suppl_pvalue-combined}
  \end{equation}

  The p-value merging and consensus method in \ac{micone} (refer Documentation) uses Equation~\ref{eqn:suppl_covariance-pvalues} to estimate the covariance of the p-values and Equation~\ref{eqn:suppl_pvalue-combined} to merge the p-values (obtained from bootstrapping) from the different correlation methods.
  Note that we do not use Pearson and Spearman methods in the p-value merging step and these algorithms are only used for demonstration and comparison.
  The combined p-values are used to threshold for significance during the consensus network step.
